{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-26 draft.tex
Long Abstract Added

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical application of embedded systems in that most of the embedded systems already includes image acquisition pipeline and a tremendous amount of progresses on research has been made. However, to successfully deploy a computer vision algorithm on any existing embedded systems, a vision algorithm needs to satisfy some criteria: minimal, manual intervention after deployment and small footprint of computing resource consumption and executable size. This criteria assumes the performance of the algorithm is reasonably good. To this end, in this paper, we propose an ensemble of the kernelized correlation filters (KCF), aka EnKCF, for a single-target object tracking. In particular, we developed a
committee of KCFs to specifically address the scale-change and the translation over frames in an independent manner. Scale and translation tasks are distributed to this group of KCFs in a way to keep the frame rate per second as high as a single naive KCF tracker without scale adaptation module. In addition, we devised a Bayes filter to minimize the gap of interactions between KCFs. It is well known that an online, model-free tracker like ours is prone to drift over time. To cope with such drifts, we developed a re-detection module that reliably identifies when to lose the target, hand-picks a small number of object proposals from existing object proposal methods (e.g., "Edge Box"), and re-initializes the track to track the object for a longer period. The proposed EnKCF tracker also leads to a more robust re-detection module then a naive KCF as it includes target-only area scale filter and target+background area translation filters with different feature modalities which can be used to search for the target box among the object proposals. To verify the usefulness of the proposed method, we compared the performance of ours to those of existing other online high speed tracking methods. Experimental results showed that the performance of our tracker are $72.53\%$ precision at $20$ px, $52.90\%$ area under the success curve (AUC) for OTB100 data and $55.71\%$ and $41.71\%$ for UAV123 data. This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in precision at $20$ px and $10\%$-$20\%$ in AUC. These numbers also compete well with other scale adaptive lower speed trackers such as SAMF, DSST, and Struct. Finally, our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
\end{abstract}
